Visualization and analysis of probability distributions of large temporal data

### 2021-11-08 Rmd/00-d-acknowlegements.Rmd
add Peter

Rob and Di are phenomenal leaders in their respective fields who lead by example. I am inspired by their creativity, wisdom, discipline, and dedication to contribute to the society through their research. Thank you for constantly pushing me to improve as a programmer and researcher and regularly sharing good practices for conducting research. Looking back, I am grateful for how my thoughts and work in statistical computing, graphics, and data analytics, in general, have evolved over the years. I still have a lot to learn, but I am a much more self-reliant and independent researcher than when I started. Di has been instrumental in exposing me to the potential benefits of effective data visualization. As a female researcher, I am encouraged by her willingness to pursue unconventional avenues and have frequently noticed her make conscious and proactive choices to question existing stereotypes and biases. Thank you, Di, for being a fantastic female role model.

@@

 <!-- - PhD friends and R community -->
Thank you, Stephanie and Nicholas Tierney, for being so warm, kind and welcoming when I began my PhD. Being a part of such an inclusive environment meant a lot to me as an international student. Thank you, Nicholas Spyrison and Mitchell O'Hara-Wild, for the numerous informative discussions, brainstorming sessions, as well as for generously sharing your expertise and experience in software development. Thank you to each of you, NUMBATs, and the broader R community for directly and indirectly helping me countless times. You never fail to inspire me.

>>>>

I am deeply grateful to my supervisors Rob J Hyndman and Dianne Cook, who are phenomenal leaders in their respective fields and lead by example. I am inspired by their creativity, wisdom, discipline, and dedication to contribute to the society through their research. Thank you for constantly pushing me to improve as a programmer and researcher and regularly sharing good practices for conducting research. Looking back, I am grateful for how my thoughts and work in statistical computing, graphics, and data analytics, in general, have evolved over the years. I still have a lot to learn, but I am a much more self-reliant and independent researcher than when I started. Di has been instrumental in exposing me to the potential benefits of effective data visualization. As a female researcher, I am encouraged by her willingness to pursue unconventional avenues and have frequently noticed her make conscious and proactive choices to question existing stereotypes and biases. Thank you, Di, for being a fantastic female role model. I would also like to express my gratitude to my supervisor Dr. Peter Toscas of Data61 CSIRO, for always being available to help with technical issues and offering feedback on practical elements of analyzing smart meter data at our monthly meetings.

@@

 <!-- - PhD friends and R community -->
Thank you, Stephanie Kobakian and Nicholas Tierney, for being so warm, kind and welcoming when I began my PhD. Being a part of such an inclusive environment meant a lot to me as an international student. Thank you, Nicholas Spyrison and Mitchell O'Hara-Wild, for the numerous informative discussions, brainstorming sessions, as well as for generously sharing your expertise and experience in software development. Thank you to each of you, NUMBATs, and the broader R community for directly and indirectly helping me countless times. You never fail to inspire me.
